### 2021-02-23 evaluation.tex
Clarify how the problem set is split
following Jelle's remarks.

The problems in $\ProblemsTptp$ are split roughly in half to form the train set and the validation set.
Both training and validation sets are restricted to problems whose graph representation consists of at most \num{100000} nodes
to limit the memory requirements of the training.
The train set is further restricted to problems that correspond to at least one training example.
In total there are \num{7648} problems in the validation set $\ProblemsVal$
and \num{2571} problems in the train set $\ProblemsTrain$.
\todo{MS: A kdyz pouzivas validation set behem uceni, ma taky mensi podmnozinu s limitem \num{100000} nodes?}
\todo{FB: Unify the terminology: validation, or train set?
MS: Co by znamenalo unify? Nebo myslis test set?}
% /home/filip/projects/vampire-ml/vampire-ml/outputs/2021-02-11/16-27-02/results.csv
% all: 17053
% train: 8527
% val: 8526
% with_questions: 5349
% graphified (not all attempted): 10219
% train&with_questions: 2647
% train&with_questions&graphified: 2571
% val&graphified: 7648

>>>>

The \num{17053} problems in $\ProblemsTptp$ are first split roughly in half to form the training set and the validation set.
Next, both training and validation sets are restricted
to problems whose graph representation consists of at most \num{100000} nodes
to limit the memory requirements of the training.
Approximately \SI{90}{\percent} of the problems fit into this limit
%a total of \num{15282} out of the \num{17053} (approximately \SI{90}{\percent}) problems satisfy this requirement.
and there are \num{7648} problems in the resulting validation set $\ProblemsVal$.
The training set $\ProblemsTrain$ is further restricted to problems that correspond to at least one training example,
leaving \num{2571} problems when training predicate precedence recommender,
and \num{1953} problems when training function precedence recommender.
\todo{FB: Unify the terminology: validation, or train set?
MS: Co by znamenalo unify? Nebo myslis test set?}
% /home/filip/projects/vampire-ml/vampire-ml/outputs/2021-02-11/16-27-02/results.csv
% all: 17053
% train: 8527
% val: 8526
% with_questions: 5349
% graphified: 15282
% train&with_questions: 2647
% train&with_questions&graphified: 2571
% val&graphified: 7648
